nextflu: Real-time tracking of seasonal influenza H3N2 virus evolution in humans

### 2015-04-01 manuscript/nextflu.tex
Add affiliation and revise abstract.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Tracking of seasonal influenza H3N2 virus evolution]{nextflu: Real-time tracking of seasonal influenza H3N2 virus evolution in humans}
\author{Trevor Bedford$^{1}$ and Richard~A.~Neher$^{2}$} % I don't care about the order
\address{$^{2}$Max Planck Institute for Developmental Biology, 72076 T\"ubingen,
Germany}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract} \section{Motivation:} Seasonal influenza viruses evolve
rapidly and change their antigenic properties. This allows the virus
population to evade immunity in their human hosts and reinfect previously
infected individuals. Similarly, vaccines against seasonal influenza need to
be updated frequently to protect against evolving virus population.

\section{Results:} We have developed a processing pipeline and web-browser
based visualization that allows convenient exploration and analysis of the
most recent influenza virus sequence data. This web-application is live at
\url{nextflu.org} and displays a phylogenetic tree that can be decorated with
several layers of additional information such the viral genotype at specific
sites, sampling location, and sequence or tree based statistics that have been
shown to predictive of future virus dynamics.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[Tracking of seasonal influenza H3N2 virus evolution]{nextflu: Real-time 
tracking of seasonal influenza H3N2 virus evolution in humans}
\author{Richard~A.~Neher$^{1}$ and Trevor Bedford$^{2}$}
\address{$^{1}$Max Planck Institute for Developmental Biology, 72076 T\"ubingen, 
Germany, and $^{2}$Vaccine and Infectious Disease Division, Fred Hutchinson
Cancer Research Center, Seattle, WA 98109, USA}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXXX}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract} \section{Motivation:} Seasonal influenza viruses evolve
rapidly and change their antigenic properties. This allows the virus
population to evade immunity in their human hosts and reinfect previously
infected individuals. Similarly, vaccines against seasonal influenza need to
be updated frequently to protect against an evolving virus population.

\section{Results:} We have developed a processing pipeline and web-browser
based visualization that allows convenient exploration and analysis of the
most recent influenza virus sequence data. This web-application is live at
\url{nextflu.org} and displays a phylogenetic tree that can be decorated with
additional information such the viral genotype at specific
sites, sampling location, and sequence or tree based statistics that have been
shown to predictive of future virus dynamics. Additionally, mutation frequency
trajectories are calculated and displayed.
